Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2018-12-07 v1-task-relevance-cspc.Rmd
in progress

class             : "man"
output:
 bookdown::html_document2:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    code_folding: hide
#    css: webpaper.css

header-includes:
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\onehalfspacing}
  - \AtBeginEnvironment{lltable}{\onehalfspacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1}}
  - \setlength{\skip\footins}{1cm}
  - \setlength{\footnotesep}{0.5cm}

#output:
#  papaja::apa6_pdf
---

```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
#options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)
```

#Introduction

@@

To date, we are aware of only one study that has looked at task-relevance within the CSPC literature. Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe. Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency. In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions. In the second, participants were given a secondary task to count the number of trials that contained a square. The first experiment failed to find evidence for context-specificity, whereas the second did. Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, & Lupiáñez [-@canadas_social_2013]) found similar effects. In this study they used images of male and female faces as context cues in a flanker task. When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not. These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.

#The Current Study

@@

#Methods

@@

```{r figure1, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
knitr::include_graphics("images/Task.jpg")
```

##Participants

@@

##Apparatus & Stimuli

@@

##Procedure

@@

#Results

@@

```{r figure2, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
knitr::include_graphics("images/E1_bar.jpg")
```

Participants with mean error rates greater than 25% were excluded from the analyses, eliminating fourteen participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994]. This procedure removed 3.76% of the total observations.
The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, F(1,128) = 8.76, *MSE* = 1672.8, *p* = .004, η~p~2 = .06, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, F(2,128) = .01, *MSE* = 1672.8, *p* = .99, η~p~2 < .0001, showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, η~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, η~p~2 = .01. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

#General Discussion

@@

#References

>>>>

class             : "man"
# output:
#  bookdown::html_document2:
#     toc: true
#     toc_float: true
#     collapsed: false
#     number_sections: false
#     toc_depth: 2
#     code_folding: hide
#     css: webpaper.css

output:
 papaja::apa6_pdf
---

```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
# options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)

library("dplyr")
library("afex")
library("papaja")
```

#  Introduction

@@

To date, we are aware of only one study that has looked at task-relevance within the CSPC literature. Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe. Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency. In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions. In the second, participants were given a secondary task to count the number of trials that contained a square. The first experiment failed to find evidence for context-specificity, whereas the second did. Although not testing task-relevance directly, [-@canadas_social_2013]) found similar effects. In this study they used images of male and female faces as context cues in a flanker task. When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not. These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.

# The Current Study

@@

# Methods

@@

```{r figure1, echo=FALSE, fig.cap='(ref:figure1)', out.width = "75%", fig.align="center"}
knitr::include_graphics("images/Task.jpg")
```

## Participants

@@

## Apparatus & Stimuli

@@

## Procedure

@@

# Results

```{r analysis}
source("data-analysis/analysis.R")

```

@@

```{r figure2, echo=FALSE, fig.cap='(ref:figure2)', out.width = "75%", fig.align="center"}
knitr::include_graphics("images/E1_bar.jpg")
```

Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed` participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994]. This procedure removed `r round(percent_removed*100,digits = 2)`% of the total observations.

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$countProp_trialCongruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant,  showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, $\eta$~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, $\eta$~p~2 = .01. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

# General Discussion

@@

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
